---
title: "SocPop Analysis"
date: "8/9/2019"
output: html_document
---

---
Import necessary packages
---
```{r setup, include=FALSE}
library(tidyverse)
library(gridExtra)
library(brms)
library(knitr)
library(ggthemes)
library(bayesplot)
library(broom)
library(readxl)
library(ggpubr)

opts_chunk$set(echo=TRUE,
              warning=FALSE, message=FALSE,
              cache=FALSE)
```

## Read in data and create one dataframe with demographic and outcome information, assuming you already ran data_wrangling!
```{r}
data_label <- read_csv("./data/data_label.csv") %>% 
  select(-X1 )
# comment_label <- read_csv("./data/comment_label.csv")

data <- read_excel("./data/data_children_n43.xlsx") %>% 
  mutate(id = as.character(id)) %>% 
  select(c(id, child_born_US, L1PRE_dad_birth_country, L1PRE_mom_ed,
           L1PRE_hi, L1POST_hi,
           L1PRE_gooddrt, L1PRE_drtn, L1POST_gooddrt, L1POST_drtn,
           L1PRE_cdi_age, L1PRE_cdi_vocab, L1POST_cdi_age, L1POST_cdi_vocab)) %>% 
  rename("rt_18m" = "L1PRE_gooddrt", "cdi_18m" = "L1PRE_cdi_vocab",
         "rt_25m" = "L1POST_gooddrt", "cdi_25m" = "L1POST_cdi_vocab",
         "ses" = "L1PRE_hi")


# merge into 1 dataframe
socpop <- data_label %>% 
  full_join(data, by = "id") %>% 
  filter(id != 435)# waiting for data to be coded
```

## Visualizing raw correlations

```{r}
socpop%>%
  select(id, gestures, labels,labels_w_gestures, rt_25m, cdi_25m)%>%
  gather(DV, y, -id, -gestures,-labels_w_gestures, -labels)%>%
  gather(input, freq, -id, -DV, -y)%>%
  ggplot(aes(x = freq, y = y))+
  geom_point()+
  facet_grid(DV~input, scales = "free")+
  geom_smooth(method = "lm")+
  stat_cor(method = "pearson")+
  theme_few()
  

```


## Models

### Reaction time as dependent variable

```{r}
# Prepare data file
# center predictors at 0 by subtracting mean to facilitate model fitting
# remove lines with NAs to allow centering

data_model <- socpop %>%
  filter(rt_25m != "NA",
         gestures != "NA",
         labels != "NA")%>%
  mutate(gestures = gestures - mean(gestures),
         labels = labels - mean(labels),
         labels_w_gestures = labels_w_gestures - mean(labels_w_gestures),
         rt_18m = rt_18m - mean(rt_18m),
         ses = ses - mean(ses))

```

#### Plotting DV

```{r}
# inspect DV - looks fine in this case
ggplot(data_model, aes(x=rt_25m))+
  geom_density()+
  xlim(0,2000)+
  theme_few()
```

#### Models RT

```{r}
# run models only when new data is added
# otherwise, you can just load the saved model output 
# saves time, each model takes approx. 2 min to run 
# when you run the model, the output is automatically saved
# even if you run the model, you need to load the saved file afterwards


# model_rt_label <- brm(rt_25m ~ labels + ses + rt_18m,
#                     data = data_model, family = gaussian(),
#           control = list(adapt_delta = 0.99),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_rt_label.rds")

model_rt_label <- readRDS("saves/model_rt_label.rds")

# model_rt_gesture <- brm(rt_25m ~ gestures + ses + rt_18m,
#                     data = data_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_rt_gesture.rds")

model_rt_gesture <- readRDS("saves/model_rt_gesture.rds")

# model_rt_label_gesture <- brm(rt_25m ~ labels + gestures + ses + rt_18m,
#                     data = data_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_rt_label_gesture.rds")

model_rt_label_gesture <- readRDS("saves/model_rt_label_gesture.rds")

# model_rt_label_gesture_int <- brm(rt_25m ~ labels * gestures + ses + rt_18m,
#                     data = data_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_rt_label_gesture_int.rds")

model_rt_label_gesture_int <- readRDS("saves/model_rt_label_gesture_int.rds")

# model_rt_overlap <- brm(rt_25m ~ labels_w_gestures + ses + rt_18m,
#                     data = data_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_rt_overlap.rds")

model_rt_overlap <- readRDS("saves/model_rt_overlap.rds")

```

#### Model comparison

```{r}
# WAIC scores for each model
waic <- loo_compare(model_rt_label, 
                    model_rt_gesture,
                    model_rt_label_gesture,
                    model_rt_label_gesture_int,
                    model_rt_overlap, 
                    criterion = "waic")%>%
  as_tibble()%>%
  select(waic, se_waic)%>%
  round(2)

# WAIC weights
weights <-model_weights(model_rt_label, 
                    model_rt_gesture,
                    model_rt_label_gesture,
                    model_rt_label_gesture_int,
                    model_rt_overlap, 
                    weight = "waic")%>%
  as_tibble()%>%
  round(6)

```

```{r}
# inspect trace plots for models
# looks fine, check again when new data was added

# plot(model_rt_label)
# 
# plot(model_rt_gesture)
# 
# plot(model_rt_label_gesture)
# 
# plot(model_rt_label_gesture_int)
# 
# plot(model_rt_overlap)
```

#### Visualizing results

```{r}
# overview over model predictors
# removing intercept because it's on a different scale
# select models depending on results of model comparison

bind_rows(
tidy(model_rt_label)%>%mutate(model = "label"),
tidy(model_rt_gesture)%>%mutate(model = "gesture"),
tidy(model_rt_overlap)%>%mutate(model = "overlap"),
tidy(model_rt_label_gesture)%>%mutate(model = "label+gesture"),
tidy(model_rt_label_gesture_int)%>%mutate(model = "label*gesture")
) %>%
  filter(term != "Intercept",
         term != "b_Intercept",
         term != "sigma",
         term != "temp_Intercept",
         term != "lp__")%>% 
  mutate(term = str_remove(term,"b_"))%>%
  ggplot(aes(term, estimate, ymin = lower, ymax = upper, color = model)) + 
  geom_hline(yintercept=0)+
  geom_pointrange(position = position_dodge(width = .8))+
  coord_flip()+
  theme_few()+
  scale_color_ptol(name = "Model")
  
```

#### Bayes Factors
```{r}

bf_rt_1 <- bayes_factor(model_rt_label, model_rt_gesture, log = F)
bf_rt_2 <- bayes_factor(model_rt_label, model_rt_overlap, log = F)
bf_rt_3 <- bayes_factor(model_rt_label, model_rt_label_gesture, log = F)
bf_rt_4 <- bayes_factor(model_rt_label, model_rt_label_gesture_int, log = F)


```

#### Overview table

```{r}
# Putting things together in a dataframe
# BF = Bayes factor in favor of the winning model in this case label
data_frame(
  model = c("label","gesture","label+gesture", "label*gesture","overlap"),
  WAIC = c(waic$waic[1],waic$waic[2],waic$waic[3],waic$waic[4],waic$waic[5]),
  SE = c(waic$se_waic[1],waic$se_waic[2],waic$se_waic[3],waic$se_waic[4],waic$se_waic[5]),
  weight = c(weights$value[1],weights$value[2],weights$value[3],weights$value[4],weights$value[5]),
  bf = c("-",round(bf_rt_1$bf,2),round(bf_rt_3$bf,2),round(bf_rt_4$bf,2),round(bf_rt_2$bf,2)))%>%
  saveRDS("saves/rt_overview.rds")

readRDS("saves/rt_overview.rds")

```



### CDI as dependent variable

```{r}
# Prepare data file
# center predictors at 0 by subtracting mean to facilitate model fitting
# remove lines with NAs to allow centering

data_cdi_model <- socpop %>%
  filter(cdi_25m != "NA",
         gestures != "NA",
         labels != "NA")%>%
  mutate(gestures = gestures - mean(gestures),
         labels = labels - mean(labels),
         labels_w_gestures = labels_w_gestures - mean(labels_w_gestures),
         cdi_18m = cdi_18m - mean(cdi_18m),
         ses = ses - mean(ses))
```

#### Plotting DV

```{r}
# inspect DV - looks fine in this case
ggplot(data_cdi_model, aes(x=cdi_25m))+
  geom_histogram(bins = 50)+
  xlim(-10,1000)+
  theme_few()
```

#### Models CDI

```{r}
# run models only when new data is added
# otherwise, you can just load the saved model output
# saves time, each model takes approx. 2 min to run
# when you run the model, the output is automatically saved
# even if you run the model, you need to load the saved file afterwards


# model_cdi_label <- brm(cdi_25m ~ labels + ses +cdi_18m,
#                     data = data_cdi_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_cdi_label.rds")

model_cdi_label <- readRDS("saves/model_cdi_label.rds")

# model_cdi_gesture <- brm(cdi_25m ~ gestures + ses+cdi_18m,
#                     data = data_cdi_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_cdi_gesture.rds")

model_cdi_gesture <- readRDS("saves/model_cdi_gesture.rds")

# model_cdi_label_gesture <- brm(cdi_25m ~ labels + gestures + ses+cdi_18m,
#                     data = data_cdi_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_cdi_label_gesture.rds")

model_cdi_label_gesture <- readRDS("saves/model_cdi_label_gesture.rds")

# model_cdi_label_gesture_int <- brm(cdi_25m ~ labels * gestures + ses+cdi_18m,
#                     data = data_cdi_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_cdi_label_gesture_int.rds")

model_cdi_label_gesture_int <- readRDS("saves/model_cdi_label_gesture_int.rds")

# model_cdi_overlap <- brm(cdi_25m ~ labels_w_gestures + ses+cdi_18m,
#                     data = data_cdi_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_cdi_overlap.rds")

model_cdi_overlap <- readRDS("saves/model_cdi_overlap.rds")

```

#### Model comparison

```{r}
# WAIC scores for each model
waic_cdi <- loo_compare(model_cdi_label, 
                    model_cdi_gesture,
                    model_cdi_label_gesture,
                    model_cdi_label_gesture_int,
                    model_cdi_overlap, 
                    criterion = "waic")%>%
  as_tibble()%>%
  select(waic, se_waic)%>%
  round(2)

# WAIC weights
weights_cdi <-model_weights(model_cdi_label, 
                    model_cdi_gesture,
                    model_cdi_label_gesture,
                    model_cdi_label_gesture_int,
                    model_cdi_overlap, 
                    weight = "waic")%>%
  as_tibble()%>%
  round(2)
```

```{r}
# inspect trace plots for models
# looks fine, check again when new data was added

# plot(model_rt_label)
# 
# plot(model_rt_gesture)
# 
# plot(model_rt_label_gesture)
# 
# plot(model_rt_label_gesture_int)
# 
# plot(model_rt_overlap)
```

#### Visualizing results

```{r}
# overview over model predictors
# removing intercept because it's on a different scale
# select models depending on results of model comparison

bind_rows(
tidy(model_cdi_label)%>%mutate(model = "label"),
tidy(model_cdi_gesture)%>%mutate(model = "gesture"),
tidy(model_cdi_overlap)%>%mutate(model = "overlap"),
tidy(model_cdi_label_gesture)%>%mutate(model = "label+gesture"),
tidy(model_cdi_label_gesture_int)%>%mutate(model = "label*gesture")
) %>%
  filter(term != "Intercept",
         term != "b_Intercept",
         term != "sigma",
         term != "temp_Intercept",
         term != "lp__")%>% 
  mutate(term = str_remove(term,"b_"))%>%
  ggplot(aes(term, estimate, ymin = lower, ymax = upper, color = model)) + 
  geom_hline(yintercept=0)+
  geom_pointrange(position = position_dodge(width = .8))+
  coord_flip()+
  theme_few()+
  scale_color_ptol(name = "Model")
  
```

#### Bayes Factors
```{r}

bf_cdi_1 <- bayes_factor(model_cdi_overlap, model_cdi_label, log = F)
bf_cdi_2 <- bayes_factor(model_cdi_overlap, model_cdi_gesture, log = F)
bf_cdi_3 <- bayes_factor(model_cdi_overlap, model_cdi_label_gesture, log = F)
bf_cdi_4 <- bayes_factor(model_cdi_overlap, model_cdi_label_gesture_int, log = F)


```

#### Overview table

```{r}
# Putting things together in a dataframe
# BF = Bayes Factor in favor of the winning model, in this case overlap
data_frame(
  model = c("label","gesture","label+gesture", "label*gesture","overlap"),
  WAIC = c(waic_cdi$waic[1],waic_cdi$waic[2],waic_cdi$waic[3],waic_cdi$waic[4],waic_cdi$waic[5]),
  SE = c(waic_cdi$se_waic[1],waic_cdi$se_waic[2],waic_cdi$se_waic[3],waic_cdi$se_waic[4],waic_cdi$se_waic[5]),
  weight = c(weights_cdi$value[1],weights_cdi$value[2],weights_cdi$value[3],weights_cdi$value[4],weights_cdi$value[5]),
  bf = c(round(bf_cdi_1$bf,2),round(bf_cdi_2$bf,2),round(bf_cdi_3$bf,2),round(bf_cdi_4$bf,2), "-"))%>%
  saveRDS("saves/cdi_overview.rds")

readRDS("saves/cdi_overview.rds")
```







