---
title: "SocPop reliability"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(irr)

```


# Reliability

Summary: For gestures, labels, and labels_w_gestures, ICC correlations were > .88, indicating a high degree of reliability for all three measures.  

Coders were more aligned on gestures (Cohen's kappa = .88, 95% CI [.54, .98] than labels (Cohen's kappa = .99, 95% CI [.96, 1]. When we examine the absolute number of codes in the scatterplots, we can see that coder 1 was slightly more conservative than coder 2 for coding of gestures, but labels were in near perfect agreement. Overlaps (using labels_w_gestures) were also in near perfect agreement at an absolute level and had a high ICC value (Cohen's kappa = .99, 95% CI [.95, 1]), which is expected since this metric is based on the number of labels. However, the high degree of reliability in overlaps also suggests that coder 1 and coder 2 were also probably capturing the same gestures at similar points in the video (versus coder 1 and coder 2 capturing the same total gestures but at different points during the video).

### reading in data
```{r}
coder1 <- read_csv("./data/data_rel_coder1.csv", col_names = T) %>% 
  dplyr::select(-X1)

coder2 <- read_csv("./data/data_rel_coder2.csv", col_names = T) %>% 
  dplyr::select(-X1)


rel <- left_join(coder1, coder2, by = "id") %>% 
  mutate(labels_coder1 = replace_na(labels_coder1, 0), 
         labels_w_gestures_coder1 = replace_na(labels_w_gestures_coder1, 0))
```



## scatterplots
red line = perfect agreement between coder 1 and coder 2

points under the red line indicates coder 1 coded more than coder 2

points above red line indicates coder 2 coded more than coder 1

### gestures
```{r}
ggplot(rel, aes(gestures_coder1, gestures_coder2)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  geom_abline(intercept = 0, slope = 1, color = "red") + 
  labs(title = "gestures: coder 2 coded more than coder 1")

cor.test(rel$gestures_coder1, rel$gestures_coder2)
```


### labels
```{r}
ggplot(rel, aes(labels_coder1, labels_coder2)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  geom_abline(intercept = 0, slope = 1, color = "red") + 
  labs(title = "labels: near perfect agreement")

cor.test(rel$labels_coder1, rel$labels_coder2)
```


### overlaps - labels_w_gestures
```{r}
ggplot(rel, aes(labels_w_gestures_coder1, labels_w_gestures_coder2)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  geom_abline(intercept = 0, slope = 1, color = "red") + 
  labs(title = "labels_w_gestures: near perfect agreement")

cor.test(rel$labels_w_gestures_coder1, rel$labels_w_gestures_coder2)
```


## ICC calculations
### gesture
```{r}
icc(rel %>% select(gestures_coder1, gestures_coder2), model = "twoway", type = "consistency")
```

### labels
```{r}

icc(rel%>%select(labels_coder1, labels_coder2), model = "twoway", type = "consistency")

```

### overlaps - labels_w_gestures
```{r}

icc(rel %>% select(labels_w_gestures_coder1, labels_w_gestures_coder2), model = "twoway", type = "consistency")

```


