---
title: "SocPop Analysis"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(gridExtra)
library(brms)
library(knitr)
library(ggthemes)
library(bayesplot)
library(broom)
library(corrr)
library(readxl)
library(ggpubr)
library(lsr)
#library(sjPlot)

opts_chunk$set(echo=F,
              warning=FALSE, message=FALSE,
              cache=FALSE, fig.align = "center")
```

```{r}
input <- read_csv("./data/input.csv")

data <- read_excel("./data/data_children_n42.xlsx") %>% 
  mutate(id = as.character(id)) %>% 
  select(c(id, L1PRE_mom_ed,
           L1PRE_hi, L1POST_hi,
           L1PRE_gooddrt, L1POST_gooddrt,
           L1PRE_cdi_age, L1PRE_cdi_vocab, L1POST_cdi_age, L1POST_cdi_vocab, 
           L1PRE_PS_AWChr)) %>% 
  rename(rt_18m = L1PRE_gooddrt, cdi_18m = L1PRE_cdi_vocab,
         rt_25m = L1POST_gooddrt, cdi_25m = L1POST_cdi_vocab,
         ses_18m = L1PRE_hi, ses_25m = L1POST_hi, awc_phr_18m = L1PRE_PS_AWChr, 
         mom_ed_18m = L1PRE_mom_ed, 
         cdi_age_18m = L1PRE_cdi_age, cdi_age_25m = L1POST_cdi_age)

# merge into 1 dataframe
socpop <- input %>% 
  full_join(data, by = "id")%>%
  select(-X1)%>%
  mutate(cdi_25m = as.numeric(cdi_25m),
         cdi_18m = as.numeric(cdi_18m),
         labels_me_rel = labels - labels_w_rel_gestures,
         labels_me = labels - labels_w_gestures,
         prop_lab_ges = labels_w_gestures/labels)

```

# Visualizing raw correlations

### Within predictors

```{r}
# I added the LENA AWC count to see if total labels is related to just parents talking more overall in the play sessions, which it is (like we would expect)

socpop%>%
  select(gestures, labels, labels_me,labels_w_gestures, labels_w_rel_gestures, awc_phr_18m)%>%
  corrr::correlate()%>%
  gather(task, cor, -rowname)%>%
  mutate(cor = replace(cor, duplicated(cor), NA),
         rowname = fct_relevel(factor(rowname), levels = c("gestures", "labels", "labels_me","labels_w_gestures", "labels_w_rel_gestures", "awc_phr_18m")))%>%
  mutate_if(is.numeric, round, digits = 2)%>%
  na.omit()%>%
  ggplot(., aes(x = rowname, y = task, fill = cor))+
  geom_tile(color = "white")+
  labs(x = "", y = "")+
  scale_fill_gradient2(low = "#CC6677", high = "#117733", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Correlation") +
   coord_fixed()+
  theme_few(base_size = 11)+
  geom_text(aes(label = cor), color = "black", size = 3) +
  theme(legend.justification = c(1, 0),
        legend.position = c(0.5, 0.75),
        legend.direction = "horizontal",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "top", title.hjust = 0.5))

```

### Predictors vs DVs

```{r, fig.width=12, fig.height=8}
socpop %>%
  select(id, gestures, labels, labels_w_gestures,labels_w_rel_gestures,awc_phr_18m,labels_me,prop_lab_ges, rt_25m, cdi_25m)%>%
  gather(DV, y, -id, -gestures,-labels_w_gestures,-labels_w_rel_gestures,-awc_phr_18m, -labels,-labels_me,-prop_lab_ges)%>%
  gather(input, freq, -id, -DV, -y)%>%
  mutate(DV = factor(DV, levels = c("rt_25m", "cdi_25m")), 
         input = factor(input),
         y = as.numeric(y)) %>%
  ggplot(aes(x = freq, y = y))+
  geom_point()+
  facet_grid(DV~input, scales = "free", switch = "y")+
  geom_smooth(method = "lm")+
  stat_cor(method = "pearson", vjust = .5)+
  labs(y = "", x = "Frequency") + 
  theme_few(base_size = 12)+
  theme(strip.placement = "outside")
  

#ggsave("./figures/scatterplot_zero_order_correlations_long.png", height = 8, width = 18, units = "in")

```

```{r}
socpop%>%
  select(gestures, labels, labels_w_gestures,labels_w_rel_gestures,awc_phr_18m, rt_25m, cdi_25m)%>%
  corrr::correlate()%>%
  gather(task, cor, -rowname)%>%
  filter(rowname == "rt_25m" | rowname == "cdi_25m")%>%
  mutate_if(is.numeric, round, digits = 2)%>%
  na.omit()%>%
  ggplot(., aes(y = rowname, x = task, fill = cor))+
  geom_tile(color = "white")+
  labs(x = "", y = "")+
  scale_fill_gradient2(low = "#CC6677", high = "#117733", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Correlation") +
   coord_fixed()+
  theme_few(base_size = 12)+
  geom_text(aes(label = cor), color = "black", size = 3) +
  theme(#legend.justification = c(1, 0),
        #legend.position = c(0.55, 0.7),
        legend.position = "right",
        legend.direction = "horizontal",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "top", title.hjust = 0.5))
```

# Models

## Reaction time as dependent variable

```{r}
# Prepare data file
# center predictors at 0 by subtracting mean to facilitate model fitting
# remove lines with NAs to allow centering

data_model <- socpop %>%
  filter(rt_25m != "NA",
         gestures != "NA",
         labels != "NA")%>%
  mutate(gestures = scale(gestures, center = TRUE, scale = F),
         labels = scale(labels, center = TRUE, scale = F),
         labels_w_gestures = scale(labels_w_gestures, center = TRUE, scale = F),
         labels_w_rel_gestures = scale(labels_w_rel_gestures, center = TRUE, scale = F),
         rt_18m = scale(rt_18m, center = TRUE, scale = F),
         ses_18m = scale(ses_18m, center = TRUE, scale = F))

```

### Plotting DV

```{r}
# inspect DV - looks fine in this case
ggplot(data_model, aes(x=rt_25m))+
  geom_density()+
  xlim(0,2000)+
  theme_few()
```

### Models RT

```{r,echo= F, echo = F}
# run models only when new data is added
# otherwise, you can just load the saved model output
# saves time, each model takes approx. 2 min to run
# when you run the model, the output is automatically saved
# even if you run the model, you need to load the saved file afterwards


# model_rt_label <- brm(rt_25m ~ labels + ses_18m + rt_18m,
#                     data = data_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_rt_label.rds")

model_rt_label <- readRDS("saves/model_rt_label.rds")

 
# model_rt_gesture <- brm(rt_25m ~gestures + ses_18m + rt_18m,
#                     data = data_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#  saveRDS("saves/model_rt_gesture.rds")

model_rt_gesture <- readRDS("saves/model_rt_gesture.rds")

# model_rt_label_gesture <- brm(rt_25m ~ labels + gestures + ses_18m + rt_18m,
#                     data = data_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_rt_label_gesture.rds")

model_rt_label_gesture <- readRDS("saves/model_rt_label_gesture.rds")

 
# model_rt_label_gesture_int <- brm(rt_25m ~labels * gestures + ses_18m + rt_18m,
#                     data = data_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_rt_label_gesture_int.rds")

model_rt_label_gesture_int <- readRDS("saves/model_rt_label_gesture_int.rds")

# model_rt_overlap <- brm(rt_25m ~ labels_w_gestures + ses_18m + rt_18m,
#                     data = data_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_rt_overlap.rds")

model_rt_overlap <- readRDS("saves/model_rt_overlap.rds")


# model_rt_rel_overlap <- brm(rt_25m ~ labels_w_rel_gestures + ses_18m + rt_18m,
#                     data = data_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_rt_rel_overlap.rds")

model_rt_rel_overlap <- readRDS("saves/model_rt_rel_overlap.rds")


# model_rt_null <- brm(rt_25m ~ ses_18m + rt_18m,
#                     data = data_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_rt_null.rds")

model_rt_null <- readRDS("saves/model_rt_null.rds")

```

#### Model comparison

```{r}
# inspect trace plots for models
# looks fine, check again when new data was added

# plot(model_rt_label)
# 
# plot(model_rt_gesture)
# 
# plot(model_rt_label_gesture)
# 
# plot(model_rt_label_gesture_int)
# 
# plot(model_rt_overlap)
#
# plot(model_rt_rel_overlap)
# 
# plot(model_rt_null)
```


```{r}
# Putting things together in a dataframe
# BF = Bayes factor in favor of the winning model in this case label

loo_compare(model_rt_label, 
                    model_rt_gesture,
                    model_rt_label_gesture,
                    model_rt_label_gesture_int,
                    model_rt_overlap,
            model_rt_rel_overlap,
            model_rt_null,
            criterion = "waic")%>%
  as.data.frame()%>%
  tibble::rownames_to_column("Model")%>%
  mutate(Model = str_replace(Model, "model_rt_", ""),
         #bf = c(NA,bf_rt_1$bf,bf_rt_2$bf,bf_rt_3$bf,bf_rt_4$bf),
         #bf = round(bf,2),
         waic = round(waic, 2),
         se_waic = round(se_waic, 2),
         weight = exp(elpd_waic)/sum(exp(elpd_waic)),
         weight = round(weight, 3))%>%
  select(Model, waic, se_waic, weight)%>%
  saveRDS("saves/rt_overview.rds")

readRDS("saves/rt_overview.rds")%>%
  kable(digits = 2, caption = "Model comparison predicting RT at 25mo")

```

#### Visualizing model predictors

```{r}
# overview over model predictors
# removing intercept because it's on a different scale
# select models depending on results of model comparison

bind_rows(
tidy(model_rt_label, prob = 0.95)%>%mutate(model = "label"),
tidy(model_rt_gesture, prob = 0.95)%>%mutate(model = "gesture"),
tidy(model_rt_overlap, prob = 0.95)%>%mutate(model = "overlap"),
tidy(model_rt_rel_overlap, prob = 0.95)%>%mutate(model = "relevant_overlap"),
tidy(model_rt_label_gesture, prob = 0.95)%>%mutate(model = "label+gesture"),
tidy(model_rt_label_gesture_int, prob = 0.95)%>%mutate(model = "label*gesture"),
tidy(model_rt_null, prob = 0.95)%>%mutate(model = "null")
) %>%
  filter(term != "b_Intercept",
         term != "Intercept",
         term != "b_intercept",
         term != "sigma",
         term != "temp_Intercept",
         term != "lp__")%>% 
  mutate(term = str_remove(term,"b_"))%>%
  ggplot(aes(term, estimate, ymin = lower, ymax = upper, color = model)) + 
  geom_hline(yintercept=0, lty = 2, col = "grey")+
  geom_pointrange(position = position_dodge(width = .8), pch = 5)+
  coord_flip()+
  theme_few()+
    labs(y = "Estimate", x = "Predictor")+
  scale_color_ptol(name = "Model")
  
```

## CDI as dependent variable

```{r}
# Prepare data file
# center predictors at 0 by subtracting mean to facilitate model fitting
# remove lines with NAs to allow centering

data_cdi_model <- socpop %>%
  filter(cdi_18m != "NA",
         cdi_25m != "NA",
         gestures != "NA",
         labels != "NA")%>%
  mutate(gestures = scale(gestures, center = TRUE, scale = F),
         labels = scale(labels, center = TRUE, scale = F),
         labels_w_gestures = scale(labels_w_gestures, center = TRUE, scale = F),
         labels_w_rel_gestures = scale(labels_w_rel_gestures, center = TRUE, scale = F),
         cdi_18m = scale(cdi_18m, center = TRUE, scale = F),
         ses_18m = scale(ses_18m, center = TRUE, scale = F))
```

### Plotting DV

```{r}
# inspect DV - looks fine in this case
ggplot(data_cdi_model, aes(x=cdi_25m))+
  geom_density()+
  xlim(0,1000)+
  theme_few()
```

### Models CDI

```{r, echo = F}
# run models only when new data is added
# otherwise, you can just load the saved model output
# saves time, each model takes approx. 2 min to run
# when you run the model, the output is automatically saved
# even if you run the model, you need to load the saved file afterwards

 
# model_cdi_label <- brm(cdi_25m ~ labels + ses_18m +cdi_18m,
#                     data = data_cdi_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_cdi_label.rds")
# 
 model_cdi_label <- readRDS("saves/model_cdi_label.rds")
# 
# model_cdi_gesture <- brm(cdi_25m ~ gestures + ses_18m +cdi_18m,
#                     data = data_cdi_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_cdi_gesture.rds")
# 
 model_cdi_gesture <- readRDS("saves/model_cdi_gesture.rds")
# 
#  
# model_cdi_label_gesture <- brm(cdi_25m ~ labels + gestures + ses_18m +cdi_18m,
#                     data = data_cdi_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_cdi_label_gesture.rds")
# 
 model_cdi_label_gesture <- readRDS("saves/model_cdi_label_gesture.rds")
# 
#  
# model_cdi_label_gesture_int <- brm(cdi_25m ~ labels * gestures + ses_18m +cdi_18m,
#                     data = data_cdi_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_cdi_label_gesture_int.rds")
# 
 model_cdi_label_gesture_int <- readRDS("saves/model_cdi_label_gesture_int.rds")
# 
# 
# model_cdi_overlap <- brm(cdi_25m ~ labels_w_gestures + ses_18m + cdi_18m,
#                     data = data_cdi_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_cdi_overlap.rds")
# 
 model_cdi_overlap <- readRDS("saves/model_cdi_overlap.rds")
# 
# 
# model_cdi_rel_overlap <- brm(cdi_25m ~ labels_w_rel_gestures + ses_18m + cdi_18m,
#                     data = data_cdi_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           #prior = prior_cdi_overlap,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_cdi_rel_overlap.rds")
# 
 model_cdi_rel_overlap <- readRDS("saves/model_cdi_rel_overlap.rds")
# 
# 
# 
# model_cdi_null <- brm(cdi_25m ~  ses_18m + cdi_18m,
#                     data = data_cdi_model, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           #prior = prior_cdi_overlap,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_cdi_null.rds")
# 
 model_cdi_null <- readRDS("saves/model_cdi_null.rds")

```


#### Model comparison

```{r}
# inspect trace plots for models
# looks fine, check again when new data was added

# plot(model_rt_label)
# 
# plot(model_rt_gesture)
# 
# plot(model_rt_label_gesture)
# 
# plot(model_rt_label_gesture_int)
# 
# plot(model_rt_overlap)
#
# plot(model_rt_rel_overlap)
```

```{r}
# Putting things together in a dataframe
# BF = Bayes Factor in favor of the winning model, in this case overlap

loo_compare(model_cdi_label, 
                    model_cdi_gesture,
                    model_cdi_label_gesture,
                    model_cdi_label_gesture_int,
                    model_cdi_overlap,
            model_cdi_rel_overlap,
            model_cdi_null,
            criterion = "waic")%>%
  as.data.frame()%>%
  tibble::rownames_to_column("Model")%>%
  mutate(Model = str_replace(Model, "model_cdi_", ""),
         waic = round(waic, 2),
         se_waic = round(se_waic, 2),
         weight = exp(elpd_waic)/sum(exp(elpd_waic)),
         weight = round(weight, 3)
         #bf = c("-", round(bf_cdi_1$bf,2),round(bf_cdi_3$bf,2),round(bf_cdi_4$bf,2),round(bf_cdi_1$bf,2))
         )%>%
  select(Model, waic, se_waic, weight)%>%
  saveRDS("saves/cdi_overview.rds")


readRDS("saves/cdi_overview.rds")%>%
  kable(digits = 2, caption = "Model comparison predicting CDI at 25mo")
```

#### Visualizing model predictors

```{r}
# overview over model predictors
# removing intercept because it's on a different scale
# select models depending on results of model comparison

bind_rows(
tidy(model_cdi_label, prob = 0.95)%>%mutate(model = "label"),
tidy(model_cdi_gesture, prob = 0.95)%>%mutate(model = "gesture"),
tidy(model_cdi_overlap, prob = 0.95)%>%mutate(model = "overlap"),
tidy(model_cdi_rel_overlap, prob = 0.95)%>%mutate(model = "relevant_overlap"),
tidy(model_cdi_label_gesture, prob = 0.95)%>%mutate(model = "label+gesture"),
tidy(model_cdi_label_gesture_int, prob = 0.95)%>%mutate(model = "label*gesture"),
tidy(model_cdi_null, prob = 0.95)%>%mutate(model = "null")
) %>%
  filter(term != "Intercept",
         term != "b_Intercept",
         term != "b_intercept",
         term != "sigma",
         term != "temp_Intercept",
         term != "lp__")%>% 
  mutate(term = str_remove(term,"b_"))%>%
  ggplot(aes(term, estimate, ymin = lower, ymax = upper, color = model)) + 
  geom_hline(yintercept=0, lty = 2, col = "grey")+
  geom_pointrange(position = position_dodge(width = .8), pch = 5 )+
  coord_flip()+
  theme_few()+
    labs(y = "Estimate", x = "Predictor")+
  scale_color_ptol(name = "Model")
  
```

# Additional analysis

## Correlation between RT 18 and Vocab 25

```{r}
socpop %>%
  select(id, rt_18m, cdi_25m)%>%
  ggplot(aes(x = rt_18m, y = cdi_25m))+
  geom_point()+
  geom_smooth(method = "lm")+
  stat_cor(method = "pearson", hjust = -1.2, vjust = .5)+
  labs(y = "Vocabulary Size at 25m", x = "Speed of Processing (ms) at 18m") + 
  theme_few()+
  coord_fixed()

ggsave("./figures/scatterplot_zero_order_correlations_rt_cdi.png", height = 8, width = 12, units = "in")

```

## Correlation by gesture type

```{r, fig.width=12, fig.height=8}
socpop %>%
  select(id, gestures, iconic, point, hold_out, touch, rt_25m, cdi_25m)%>%
  gather(DV, y, -id, -gestures, -iconic, -point, -hold_out, -touch)%>%
  gather(input, freq, -id, -DV, -y)%>%
  mutate(DV = factor(DV, levels = c("rt_25m", "cdi_25m")), 
         input = factor(input, levels = c("labels", "gestures", "point", "iconic","hold_out","touch")),
         y = as.numeric(y)) %>%
  ggplot(aes(x = freq, y = y))+
  geom_point()+
  facet_grid(DV~input, scales = "free", switch = "y")+
  geom_smooth(method = "lm")+
  stat_cor(method = "pearson",  vjust = .5)+
  labs(y = " ", x = "Frequency") + 
  theme_few()

```

## Concurrent relations at 18m

### Visualizing raw correlations

```{r, fig.width=12, fig.height=8}
socpop %>%
  select(id, gestures, labels, labels_w_gestures,labels_w_rel_gestures,awc_phr_18m, rt_18m, cdi_18m)%>%
  gather(DV, y, -id, -gestures,-labels_w_gestures,-labels_w_rel_gestures,-awc_phr_18m, -labels)%>%
  gather(input, freq, -id, -DV, -y)%>%
  mutate(DV = factor(DV, levels = c("rt_18m", "cdi_18m")), 
         input = factor(input, levels = c("labels", "gestures", "labels_w_gestures", "labels_rel","labels_w_rel_gestures","awc_phr_18m")),
         y = as.numeric(y)) %>%
  ggplot(aes(x = freq, y = y))+
  geom_point()+
  facet_grid(DV~input, scales = "free", switch = "y")+
  geom_smooth(method = "lm")+
  stat_cor(method = "pearson", vjust = .5)+
  labs(y = "", x = "Frequency") + 
  theme_few()+
  theme(strip.placement = "outside")


```

```{r}
socpop%>%
  select(gestures, labels, labels_w_gestures,labels_w_rel_gestures,awc_phr_18m, rt_18m, cdi_18m)%>%
  corrr::correlate()%>%
  gather(task, cor, -rowname)%>%
  filter(rowname == "rt_18m" | rowname == "cdi_18m")%>%
  mutate_if(is.numeric, round, digits = 2)%>%
  na.omit()%>%
  ggplot(., aes(y = rowname, x = task, fill = cor))+
  geom_tile(color = "white")+
  labs(x = "", y = "")+
  scale_fill_gradient2(low = "#CC6677", high = "#117733", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Correlation") +
   coord_fixed()+
  theme_few(base_size = 12)+
  geom_text(aes(label = cor), color = "black", size = 3) +
  theme(#legend.justification = c(1, 0),
        #legend.position = c(0.55, 0.7),
        legend.position = "right",
        legend.direction = "horizontal",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "top", title.hjust = 0.5))
```

### Models

#### Reaction time as dependent variable

```{r}
# Prepare data file
# center predictors at 0 by subtracting mean to facilitate model fitting
# remove lines with NAs to allow centering

data_model_con <- socpop %>%
  filter(rt_18m != "NA",
         gestures != "NA",
         labels != "NA")%>%
  mutate(gestures = scale(gestures, center = TRUE, scale = F),
         labels = scale(labels, center = TRUE, scale = F),
         labels_w_gestures = scale(labels_w_gestures, center = TRUE, scale = F),
         labels_w_rel_gestures = scale(labels_w_rel_gestures, center = TRUE, scale = F),
         ses_18m = scale(ses_18m, center = TRUE, scale = F))

```

##### Plotting DV

```{r}
# inspect DV - looks fine in this case
ggplot(data_model_con, aes(x=rt_18m))+
  geom_density()+
  xlim(0,2000)+
  theme_few()
```

##### Models RT

```{r,echo= F}
# run models only when new data is added
# otherwise, you can just load the saved model output
# saves time, each model takes approx. 2 min to run
# when you run the model, the output is automatically saved
# even if you run the model, you need to load the saved file afterwards

# model_rt_label_con <- brm(rt_18m ~ labels + ses_18m,
#                     data = data_model_con, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_rt_label_con.rds")
# 
 model_rt_label_con <- readRDS("saves/model_rt_label_con.rds")
# 
# 
# 
# model_rt_gesture_con <- brm(rt_18m ~gestures + ses_18m,
#                     data = data_model_con, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#  saveRDS("saves/model_rt_gesture_con.rds")
# 
 model_rt_gesture_con <- readRDS("saves/model_rt_gesture_con.rds")
# 
# 
# model_rt_label_gesture_con <- brm(rt_18m ~ labels + gestures + ses_18m,
#                     data = data_model_con, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_rt_label_gesture_con.rds")
# 
 model_rt_label_gesture_con <- readRDS("saves/model_rt_label_gesture_con.rds")
# 
# 
# 
# 
# model_rt_label_gesture_int_con <- brm(rt_18m ~labels * gestures + ses_18m,
#                     data = data_model_con, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_rt_label_gesture_int_con.rds")
# 
 model_rt_label_gesture_int_con <- readRDS("saves/model_rt_label_gesture_int_con.rds")
# 
# 
# 
# model_rt_overlap_con <- brm(rt_18m ~ labels_w_gestures + ses_18m,
#                     data = data_model_con, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_rt_overlap_con.rds")
# 
 model_rt_overlap_con <- readRDS("saves/model_rt_overlap_con.rds")
# 
# 
# model_rt_rel_overlap_con <- brm(rt_18m ~ labels_w_rel_gestures + ses_18m,
#                     data = data_model_con, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_rt_rel_overlap_con.rds")
# 
 model_rt_rel_overlap_con <- readRDS("saves/model_rt_rel_overlap_con.rds")
# 
# 
# model_rt_null_con <- brm(rt_18m ~ ses_18m,
#                     data = data_model_con, family = gaussian(),
#           control = list(adapt_delta = 0.95),
#           save_all_pars = TRUE,
#           chains = 4,
#           cores = 4,
#           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_rt_null_con.rds")
# 
 model_rt_null_con <- readRDS("saves/model_rt_null_con.rds")

```

###### Model comparison

```{r}
# inspect trace plots for models
# looks fine, check again when new data was added

# plot(model_rt_label_con)
# 
# plot(model_rt_gesture_con)
# 
# plot(model_rt_label_gesture_con)
# 
# plot(model_rt_label_gesture_int_con)
# 
# plot(model_rt_overlap_con)
# 
# plot(model_rt_rel_overlap_con)
# 
# plot(model_rt_null_con)
```

```{r}
# Putting things together in a dataframe
# BF = Bayes factor in favor of the winning model in this case label

loo_compare(model_rt_label_con, 
                    model_rt_gesture_con,
                    model_rt_label_gesture_con,
                    model_rt_label_gesture_int_con,
                    model_rt_overlap_con,
            model_rt_rel_overlap_con,
            model_rt_null_con,
            criterion = "waic")%>%
  as.data.frame()%>%
  tibble::rownames_to_column("Model")%>%
  mutate(Model = str_replace(Model, "model_rt_", ""),
         #bf = c(NA,bf_rt_1$bf,bf_rt_2$bf,bf_rt_3$bf,bf_rt_4$bf),
         #bf = round(bf,2),
         waic = round(waic, 2),
         se_waic = round(se_waic, 2),
         weight = exp(elpd_waic)/sum(exp(elpd_waic)),
         weight = round(weight, 3))%>%
  select(Model, waic, se_waic, weight)%>%
  saveRDS("saves/rt_overview_con.rds")

readRDS("saves/rt_overview_con.rds")%>%
  kable(digits = 2, caption = "Model comparison predicting RT at 18mo")

```

###### Visualizing model predictors

```{r}
# overview over model predictors
# removing intercept because it's on a different scale
# select models depending on results of model comparison

bind_rows(
tidy(model_rt_label_con, prob = 0.95)%>%mutate(model = "label"),
tidy(model_rt_gesture_con, prob = 0.95)%>%mutate(model = "gesture"),
tidy(model_rt_overlap_con, prob = 0.95)%>%mutate(model = "overlap"),
tidy(model_rt_rel_overlap_con, prob = 0.95)%>%mutate(model = "relevant_overlap"),
tidy(model_rt_label_gesture_con, prob = 0.95)%>%mutate(model = "label+gesture"),
tidy(model_rt_label_gesture_int_con, prob = 0.95)%>%mutate(model = "label*gesture"),
tidy(model_rt_null_con, prob = 0.95)%>%mutate(model = "null")
) %>%
  filter(term != "b_Intercept",
         term != "Intercept",
         term != "b_intercept",
         term != "sigma",
         term != "temp_Intercept",
         term != "lp__")%>% 
  mutate(term = str_remove(term,"b_"))%>%
  ggplot(aes(term, estimate, ymin = lower, ymax = upper, color = model)) + 
  geom_hline(yintercept=0, lty = 2, col = "grey")+
  geom_pointrange(position = position_dodge(width = .8), pch = 5)+
  coord_flip()+
  theme_few()+
    labs(y = "Estimate", x = "Predictor")+
  scale_color_ptol(name = "Model")
  
```


#### CDI as dependent variable

```{r}
# Prepare data file
# center predictors at 0 by subtracting mean to facilitate model fitting
# remove lines with NAs to allow centering

data_cdi_model_con <- socpop %>%
  filter(cdi_18m != "NA",
         gestures != "NA",
         labels != "NA")%>%
  mutate(gestures = scale(gestures, center = TRUE, scale = F),
         labels = scale(labels, center = TRUE, scale = F),
         labels_w_gestures = scale(labels_w_gestures, center = TRUE, scale = F),
         labels_w_rel_gestures = scale(labels_w_rel_gestures, center = TRUE, scale = F),
         ses_18m = scale(ses_18m, center = TRUE, scale = F))
```

##### Plotting DV

```{r}
# inspect DV - looks fine in this case
ggplot(data_cdi_model_con, aes(x=cdi_18m))+
  geom_density()+
  xlim(0,1000)+
  theme_few()
```

##### Models CDI

```{r, echo = F}
# run models only when new data is added
# otherwise, you can just load the saved model output
# saves time, each model takes approx. 2 min to run
# when you run the model, the output is automatically saved
# even if you run the model, you need to load the saved file afterwards


# model_cdi_label_con <- brm(cdi_18m ~ labels + ses_18m,
#                           data = data_cdi_model_con, family = gaussian(),
#                           control = list(adapt_delta = 0.95),
#                           save_all_pars = TRUE,
#                           chains = 4,
#                           cores = 4,
#                           iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_cdi_label_con.rds")
# 
 model_cdi_label_con <- readRDS("saves/model_cdi_label_con.rds")
# 
# 
# 
# model_cdi_gesture_con <- brm(cdi_18m ~gestures + ses_18m,
#                             data = data_cdi_model_con, family = gaussian(),
#                             control = list(adapt_delta = 0.95),
#                             save_all_pars = TRUE,
#                             chains = 4,
#                             cores = 4,
#                             iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_cdi_gesture_con.rds")
# 
 model_cdi_gesture_con <- readRDS("saves/model_cdi_gesture_con.rds")
# 
# 
# model_cdi_label_gesture_con <- brm(cdi_18m ~ labels + gestures + ses_18m,
#                                   data = data_cdi_model_con, family = gaussian(),
#                                   control = list(adapt_delta = 0.95),
#                                   save_all_pars = TRUE,
#                                   chains = 4,
#                                   cores = 4,
#                                   iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_cdi_label_gesture_con.rds")
# 
 model_cdi_label_gesture_con <- readRDS("saves/model_cdi_label_gesture_con.rds")
# 
# 
# 
# 
# model_cdi_label_gesture_int_con <- brm(cdi_18m ~labels * gestures + ses_18m,
#                                       data = data_cdi_model_con, family = gaussian(),
#                                       control = list(adapt_delta = 0.95),
#                                       save_all_pars = TRUE,
#                                       chains = 4,
#                                       cores = 4,
#                                       iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_cdi_label_gesture_int_con.rds")
# 
 model_cdi_label_gesture_int_con <- readRDS("saves/model_cdi_label_gesture_int_con.rds")
# 
# 
# 
# model_cdi_overlap_con <- brm(cdi_18m ~ labels_w_gestures + ses_18m,
#                             data = data_cdi_model_con, family = gaussian(),
#                             control = list(adapt_delta = 0.95),
#                             save_all_pars = TRUE,
#                             chains = 4,
#                             cores = 4,
#                             iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_cdi_overlap_con.rds")
# 
 model_cdi_overlap_con <- readRDS("saves/model_cdi_overlap_con.rds")
# 
# 
# model_cdi_rel_overlap_con <- brm(cdi_18m ~ labels_w_rel_gestures + ses_18m,
#                                 data = data_cdi_model_con, family = gaussian(),
#                                 control = list(adapt_delta = 0.95),
#                                 save_all_pars = TRUE,
#                                 chains = 4,
#                                 cores = 4,
#                                 iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_cdi_rel_overlap_con.rds")
# 
 model_cdi_rel_overlap_con <- readRDS("saves/model_cdi_rel_overlap_con.rds")
# 
# 
# model_cdi_null_con <- brm(cdi_18m ~ ses_18m,
#                          data = data_cdi_model_con, family = gaussian(),
#                          control = list(adapt_delta = 0.95),
#                          save_all_pars = TRUE,
#                          chains = 4,
#                          cores = 4,
#                          iter = 50000)%>%
#   add_criterion("waic")%>%
#   saveRDS("saves/model_cdi_null_con.rds")
# 
 model_cdi_null_con <- readRDS("saves/model_cdi_null_con.rds")

```


###### Model comparison

```{r}
# inspect trace plots for models
# looks fine, check again when new data was added

# plot(model_cdi_label)
# 
# plot(model_cdi_gesture)
# 
# plot(model_cdi_overlap)
# 
# plot(model_cdi_rel_overlap)
# 
# plot(model_cdi_label_gesture)
# 
# plot(model_cdi_label_gesture_int)
```

```{r}
# Putting things together in a dataframe
# BF = Bayes Factor in favor of the winning model, in this case overlap

loo_compare(model_cdi_label_con, 
                    model_cdi_gesture_con,
                    model_cdi_label_gesture_con,
                    model_cdi_label_gesture_int_con,
                    model_cdi_overlap_con,
            model_cdi_rel_overlap_con,
            model_cdi_null_con,
            criterion = "waic")%>%
  as.data.frame()%>%
  tibble::rownames_to_column("Model")%>%
  mutate(Model = str_replace(Model, "model_cdi_", ""),
         waic = round(waic, 2),
         se_waic = round(se_waic, 2),
         weight = exp(elpd_waic)/sum(exp(elpd_waic)),
         weight = round(weight, 3)
         #bf = c("-", round(bf_cdi_1$bf,2),round(bf_cdi_3$bf,2),round(bf_cdi_4$bf,2),round(bf_cdi_1$bf,2))
         )%>%
  select(Model, waic, se_waic, weight)%>%
  saveRDS("saves/cdi_overview_con.rds")


readRDS("saves/cdi_overview_con.rds")%>%
  kable(digits =2, caption = "Model comparison predicting CDI at 18mo")
```

###### Visualizing model predictors

```{r}
# overview over model predictors
# removing intercept because it's on a different scale
# select models depending on results of model comparison

bind_rows(
tidy(model_cdi_label_con, prob = 0.95)%>%mutate(model = "label"),
tidy(model_cdi_gesture_con, prob = 0.95)%>%mutate(model = "gesture"),
tidy(model_cdi_overlap_con, prob = 0.95)%>%mutate(model = "overlap"),
tidy(model_cdi_rel_overlap_con, prob = 0.95)%>%mutate(model = "relevant_overlap"),
tidy(model_cdi_label_gesture_con, prob = 0.95)%>%mutate(model = "label+gesture"),
tidy(model_cdi_label_gesture_int_con, prob = 0.95)%>%mutate(model = "label*gesture"),
tidy(model_cdi_null_con, prob = 0.95)%>%mutate(model = "null")
) %>%
  filter(term != "Intercept",
         term != "b_Intercept",
         term != "b_intercept",
         term != "sigma",
         term != "temp_Intercept",
         term != "lp__")%>% 
  mutate(term = str_remove(term,"b_"))%>%
  ggplot(aes(term, estimate, ymin = lower, ymax = upper, color = model)) + 
  geom_hline(yintercept=0, lty = 2, col = "grey")+
  geom_pointrange(position = position_dodge(width = .8), pch = 5 )+
  coord_flip()+
  labs(y = "Estimate", x = "Predictor")+
  theme_few()+
  scale_color_ptol(name = "Model")
  
```

