---
title: "SocPop reliability"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(irr)

```

#  Primary coder (coder 1)

## Read data

```{r}
gesture_coder1 <- read_csv("./data/reliability_coder1_caregiver.csv", col_names = F)%>%
  rename(start = X3,
         stop = X4,
         tier = X1,
         ant = X6, 
         file = X7)%>%
  select(file, tier, start, stop, ant)%>%
  filter(tier == "Caregiver nonlinguistic") %>% 
  mutate(id = str_sub(file, 1, 3)) %>% 
  select(-file)


label_coder1 <- read_csv("./data/reliability_coder1_caregiver.csv", col_names = F)%>%
  rename(start = X3,
         stop = X4,
         tier = X1,
         ant = X6,
         file = X7)%>%
  select(file,tier, start, stop, ant)%>%
  filter(tier == "Caregiver linguistic", 
         ant != "english") %>% 
  mutate(id = str_sub(file, 1, 3)) %>% 
  select(-file)
```

## Compute number of gestures labels and overlap (from label perspective)

```{r}
overlap_label_coder1 <-  label_coder1 %>%
  mutate(start = start -1 ,
         stop = stop + 1)%>%
  group_by(id, tier, start, stop)%>%
  expand(nesting(gesture_coder1$start, gesture_coder1$stop, gesture_coder1$id))%>%
  filter(id == `gesture_coder1$id`)%>%
  mutate(overlap_start = ifelse(start <= `gesture_coder1$start` & stop >= `gesture_coder1$start`, T,F),
         overlap_stop = ifelse(start <= `gesture_coder1$stop` & stop >= `gesture_coder1$stop`, T,F))%>%
  group_by(id, tier, start, stop)%>%
  summarise(overlap_start = sum(overlap_start),
            overlap_stop = sum(overlap_stop))%>%
  mutate(overlap = ifelse(sum(overlap_start,overlap_stop) > 0, T,F))%>%
  group_by(id)%>%
  summarise(labels_w_gestures_coder1 = sum(overlap))
         
gesture_sum_coder1 <- gesture_coder1 %>%
  group_by(id)%>%
  summarise(gestures_coder1 = n())

label_sum_coder1 <- label_coder1 %>%
  group_by(id)%>%
  summarise(labels_coder1 = n())

data_label_coder1 <- plyr::join_all(list(gesture_sum_coder1, label_sum_coder1, overlap_label_coder1), by=c("id"), type='left')
```

# Second coder (coder 2)

## Read data

```{r}
gesture_coder2 <- read_csv("./data/reliability_coder2_caregiver.csv", col_names = F)%>%
  rename(start = X3,
         stop = X4,
         tier = X1,
         ant = X6, 
         file = X7)%>%
  select(file, tier, start, stop, ant)%>%
  filter(tier == "Caregiver nonlinguistic") %>% 
  mutate(id = str_sub(file, 1, 3)) %>% 
  select(-file)


label_coder2 <- read_csv("./data/reliability_coder2_caregiver.csv", col_names = F)%>%
  rename(start = X3,
         stop = X4,
         tier = X1,
         ant = X6,
         file = X7)%>%
  select(file,tier, start, stop, ant)%>%
  filter(tier == "Caregiver linguistic", 
         ant != "english") %>% 
  mutate(id = str_sub(file, 1, 3)) %>% 
  select(-file)

```

## Compute number of gestures labels and overlap (from label perspective)

```{r}
overlap_label_coder2 <-  label_coder2 %>%
  mutate(start = start -1 ,
         stop = stop + 1)%>%
  group_by(id, tier, start, stop)%>%
  expand(nesting(gesture_coder2$start, gesture_coder2$stop, gesture_coder2$id))%>%
  filter(id == `gesture_coder2$id`)%>%
  mutate(overlap_start = ifelse(start <= `gesture_coder2$start` & stop >= `gesture_coder2$start`, T,F),
         overlap_stop = ifelse(start <= `gesture_coder2$stop` & stop >= `gesture_coder2$stop`, T,F))%>%
  group_by(id, tier, start, stop)%>%
  summarise(overlap_start = sum(overlap_start),
            overlap_stop = sum(overlap_stop))%>%
  mutate(overlap = ifelse(sum(overlap_start,overlap_stop) > 0, T,F))%>%
  group_by(id)%>%
  summarise(labels_w_gestures_coder2 = sum(overlap))
         
gesture_sum_coder2 <- gesture_coder2 %>%
  group_by(id)%>%
  summarise(gestures_coder2 = n())

label_sum_coder2 <- label_coder2 %>%
  group_by(id)%>%
  summarise(labels_coder2 = n())

data_label_coder2 <- plyr::join_all(list(gesture_sum_coder2, label_sum_coder2, overlap_label_coder2), by=c("id"), type='left')
```


# Reliability

Summary: For gestures, labels, and labels_w_gestures, ICC correlations were > .88, indicating a high degree of reliability for all three measures.  

Coders were more aligned on gestures (Cohen's kappa = .88, 95% CI [.54, .98] than labels (Cohen's kappa = .99, 95% CI [.96, 1]. When we examine the absolute number of codes in the scatterplots, we can see that coder 1 was slightly more conservative than coder 2 for coding of gestures, but labels were in near perfect agreement. Overlaps (using labels_w_gestures) were also in near perfect agreement at an absolute level and had a high ICC value (Cohen's kappa = .99, 95% CI [.95, 1]), which is expected since this metric is based on the number of labels. However, the high degree of reliability in overlaps also suggests that coder 1 and coder 2 were also probably capturing the same gestures at similar points in the video (versus coder 1 and coder 2 capturing the same total gestures but at different points during the video).

NOTE: For labels, we will want to look into the categorization of present vs. imaginary labels, because this did not seem to achieve a high level of reliability based on the ELAN inter-annotator reliability metrics. The distinction between present vs imaginary is not necessary for SOCPOP analyses.

### joining data files
```{r}
rel <- left_join(data_label_coder1, data_label_coder2, by = "id")
```



## scatterplots
red line = perfect agreement between coder 1 and coder 2

points under the red line indicates coder 1 coded more gestures than coder 2

points above red line indicates coder 2 coded more gestures than coder 1
### gestures
```{r}
ggplot(rel, aes(gestures_coder1, gestures_coder2)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  geom_abline(intercept = 0, slope = 1, color = "red") + 
  labs(title = "gestures: coder 2 coded more than coder 1")

cor.test(rel$gestures_coder1, rel$gestures_coder2)
```


### labels
```{r}
ggplot(rel, aes(labels_coder1, labels_coder2)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  geom_abline(intercept = 0, slope = 1, color = "red") + 
  labs(title = "labels: near perfect agreement")

cor.test(rel$labels_coder1, rel$labels_coder2)
```


### overlaps - labels_w_gestures
```{r}
ggplot(rel, aes(labels_w_gestures_coder1, labels_w_gestures_coder2)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  geom_abline(intercept = 0, slope = 1, color = "red") + 
  labs(title = "labels_w_gestures: near perfect agreement")

cor.test(rel$labels_w_gestures_coder1, rel$labels_w_gestures_coder2)
```


## ICC calculations
### gesture
```{r}
icc(rel %>% select(gestures_coder1, gestures_coder2), model = "twoway", type = "consistency")
```

### labels
```{r}

icc(rel%>%select(labels_coder1, labels_coder2), model = "twoway", type = "consistency")

```

### overlaps - labels_w_gestures
```{r}

icc(rel %>% select(labels_w_gestures_coder1, labels_w_gestures_coder2), model = "twoway", type = "consistency")

```


